Something About Ground Based Asteroseismology

### 2017-09-06 paper/aldebaran.tex
Paper skeleton (author names, couple of references).

\author{Guy Davies}

@@

\email{w.farr@bham.ac.uk, G.R.Davies@bham.ac.uk, Benjamin.Pope@physics.ox.ac.uk, txn016@student.bham.ac.uk}

@@

>>>>

\author{Guy R. Davies}

@@

\author{James Barrett}
\affiliation{Birmingham Institute for Gravitational Wave Astronomy,
  University of Birmingham, Birmingham, B15 2TT, United Kingdom}

\email{w.farr@bham.ac.uk, G.R.Davies@bham.ac.uk, Benjamin.Pope@physics.ox.ac.uk, txn016@student.bham.ac.uk, jimbarrett27@gmail.com}

@@

Reference \citet{Kelly2014}, compare to \citet{Foreman-Mackey2017}.
